Estimation of flow trajectories in a multi-lines network

### 2023-01-13 paper_complex_networks/paper_complex_networks_v1.tex
update notes

\subsection{Statement of the problem (version 2, added by GG)}
Let $f_{st}=n_{st}/n_{\bullet\bullet}$ be the proportion of $st$-trips (empirical distribution) and let $g_{st}$ be some prior guess on its shape (theoretical distribution). Also suppose we know the margins distribution of the real transportation flow $n^\star_{st}$, i.e. $c_s = n^\star_{s \bullet} / n^\star_{\bullet \bullet}$ and $d_t = n^\star_{\bullet t} / n^\star_{\bullet \bullet}$. We are interested in finding
\begin{align}
	\label{constr_MaxEnt}
	\min_{\mathbf{f}\in\mathcal{F}} &\; \sum_{st}f_{st}\log \frac{f_{st}}{g_{st}}, \notag \\
	s.t. &\; \sum_t f_{st} = c_s, \notag \\
	&\; \sum_s f_{st} = d_t.
\end{align}
The Lagragian is
\begin{equation}
	\label{Lag}
	L = \sum_{st}f_{st}\log \frac{f_{st}}{g_{st}} - \sum_s \lambda_s (c_s - \sum_t f_{st}) - \sum_t \mu_t (d_t - \sum_s f_{st}),
\end{equation}
which gives, after deriving,
\begin{equation}
	\label{Sol}
	f_{st} = \alpha_s \beta_t g_{st} \qquad \text{with } \alpha_s := \exp(- 1 - \lambda_s) \text{, } \beta_t := \exp(- \mu_t).
\end{equation}
Using constraints in (\ref{constr_MaxEnt}), we find
\begin{equation}
	\label{Sol_LagMult}
	\alpha_s = \frac{c_s}{\sum_t \beta_t g_{st}}, \qquad \beta_t = \frac{d_t}{\sum_s \alpha_s g_{st}}, 
\end{equation}
which gives an \emph{iterative fitting algorithm}
\begin{equation}
	\label{Iterative fitting}
	\alpha^{(\iota)}_s = \frac{c_s}{\sum_t \beta^{(\iota)}_t g_{st}}, \qquad \beta^{(\iota + 1)}_t = \frac{d_t}{\sum_s \alpha^{(\iota)}_s g_{st}}, 
\end{equation}

>>>>

\subsection{Statement of the problem (version 2, added by GG)}
Let $f_{st}=n_{st}/n_{\bullet\bullet}$ be the proportion of $st$-trips (empirical distribution) and let $g_{st}$ be some prior guess on its shape (theoretical distribution). Also suppose a prior guess of row and margin constraints for $f_{st}$, respectively $c_s$ and $d_t$, which has to verify 
\begin{equation}
	\frac{c_i}{c_j} = \frac{a_i}{a_j} \qquad \frac{d_i}{d_j} = \frac{b_i}{b_j}  \qquad \forall i, j \text{ without junction.} \\
\end{equation}
Setting these gives us
\begin{equation}
	n_{\bullet \bullet} = \frac{c_i}{a_i} = \frac{d_i}{b_i} \qquad \forall i \text{ without junction.}  
\end{equation}
We are interested in finding
\begin{align}
	\label{constr_MaxEnt}
	\min_{\mathbf{f}\in\mathcal{F}} &\; \sum_{st}f_{st}\log \frac{f_{st}}{g_{st}}, \notag \\
	s.t. &\; \sum_t f_{st} = c_s, \notag \\
	&\; \sum_s f_{st} = d_t.
\end{align}
The Lagragian is
\begin{equation}
	L = \sum_{st}f_{st}\log \frac{f_{st}}{g_{st}} - \sum_s \lambda_s (c_s - \sum_t f_{st}) - \sum_t \mu_t (d_t - \sum_s f_{st}), \notag
\end{equation}
which gives, after deriving and setting to zero,
\begin{equation}
	\label{Sol}
	f_{st} = \alpha_s \beta_t g_{st} \qquad \text{with } \alpha_s := \exp(- 1 - \lambda_s) \text{, } \beta_t := \exp(- \mu_t).
\end{equation}
Using constraints in (\ref{constr_MaxEnt}), we find
\begin{equation}
	\label{Sol_LagMult}
	\alpha_s = \frac{c_s}{\sum_t \beta_t g_{st}}, \qquad \beta_t = \frac{d_t}{\sum_s \alpha_s g_{st}}, 
\end{equation}
which gives an \emph{iterative fitting algorithm}
\begin{equation}
	\label{Iterative fitting}
	\alpha^{(\iota)}_s = \frac{c_s}{\sum_t \beta^{(\iota)}_t g_{st}}, \qquad \beta^{(\iota + 1)}_t = \frac{d_t}{\sum_s \alpha^{(\iota)}_s g_{st}}, 
\end{equation}
